Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-07-14 jsm/speed-presentation/poster/poster.Rmd
minor tweaks

1. Decompose $A \approx V_{p,q} \Lambda_{p,q} V_{p,q}^\top$, $p = \frac{K (K+1)}{2}$ and $q = \frac{K (K-1)}{2}$.
2. Compute $B = |n V_{p,q} V_{p,q}^\top|$.
3. Construct graph $G'$ from $B$.
4. Partition $G'$ into $K$ disconnected subgraphs.

**Theorem** (KTT): 
Let $B$ be the affinity matrix from OSC. 
Then $\forall$ pairs $(i, j)$ belonging to different communities 
and sparsity factor satisfying $n \rho_n = \omega\big(\log^{4c} n\big)$,  
$\max_{i, j} B_{ij} = O_P \Big( \frac{\log^c n}{\sqrt{n \rho_n}} \Big)$.

@@

Exploiting the geometry of PABMs (and other block models) results in consistent community detection algorithms.

>>>>

1. Eigendecompose $A \approx V_{p,q} \Lambda_{p,q} V_{p,q}^\top$ with $p = \frac{K (K+1)}{2}$ and $q = \frac{K (K-1)}{2}$.
2. Compute $B = |n V_{p,q} V_{p,q}^\top|$.
3. Construct graph $G'$ from $B$.
4. Partition $G'$ into $K$ disconnected subgraphs.

**Theorem** (KTT): 
Let $B$ be the affinity matrix from OSC. 
Then $\forall$ $(i, j)$ belonging to different communities and sparsity factor satisfying $n \rho_n = \omega\big(\log^{4c} n\big),$ $\max_{i, j} B_{ij} = O_P \Big( \frac{\log^c n}{\sqrt{n \rho_n}} \Big)$.

@@

Exploiting the geometry of PABMs (and other block models) results in intuitive and consistent community detection algorithms.

### 2022-07-14 jsm/speed-presentation/slides.tex
finished poster
minor tweaks

\textbf{Theorem}:
\(\max\limits_i \|\hat{X}_i - Q_n X_i \| = O_P \Big( \frac{(\log n)^c}{n^{1/2}} \Big)\)
as \(n \to \infty\)
\end{frame}

\begin{frame}{Connecting Block Models to the (G)RDPG Model}
\protect\hypertarget{connecting-block-models-to-the-grdpg-model}{}
\begin{columns}[T]
\begin{column}{0.48\textwidth}
\begin{center}\includegraphics[width=0.5\linewidth]{slides_files/figure-beamer/unnamed-chunk-5-1} \end{center}

@@

\textbf{Theorem} (KTT): Let \(\hat{B}\) with entries \(\hat{B}_{ij}\) be
the affinity matrix from OSC. Then \(\forall\) pairs \((i, j)\)
belonging to different communities and sparsity factor satisfying
\(n \rho_n = \omega\big((\log n)^{4c}\big)\),\\
\(\max_{i, j} \hat{B}_{ij} = O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)\)
as \(n \to \infty\).

@@

\begin{frame}{Simulation Results}
\protect\hypertarget{simulation-results}{}
We compare four algorithms for community detection on randomly generated
PABMs:

>>>>

\textbf{Theorem}:
\(\max\limits_i \|\hat{X}_i - Q_n X_i \| = O_P \Big( \frac{(\log n)^c}{n^{1/2}} \Big)\).
\end{frame}

\begin{frame}{Connecting Block Models to the GRDPG Model}
\protect\hypertarget{connecting-block-models-to-the-grdpg-model}{}
\begin{columns}[T]
\begin{column}{0.48\textwidth}
\begin{center}\includegraphics[width=0.5\linewidth]{slides_files/figure-beamer/unnamed-chunk-5-1} \end{center}

@@

\textbf{Theorem} (KTT): Let \(\hat{B}\) with entries \(\hat{B}_{ij}\) be
the affinity matrix from OSC. Then \(\forall\) pairs \((i, j)\)
belonging to different communities and sparsity factor satisfying
\(n \rho_n = \omega\big((\log n)^{4c}\big)\),\\
\(\max_{i, j} \hat{B}_{ij} = O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)\).

@@

\begin{frame}{Simulation Study}
\protect\hypertarget{simulation-study}{}
We compare four algorithms for community detection on randomly generated
PABMs:
